Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-06 documentation/paper.tex
Added graph for ICN accuracy by run

During a grid search of these parameters (in addition to regularization parameters of the network), the best accuracy achieved for replication of Acoustic Parameter was exactly 100\%. The mean of all epochs within that training run was 98\%. Further demonstrating this is a powerful algorithm and that high performance was not a one-off, 35\% of the training runs replicated Acoustic Parameter with a mean accuracy greater than 92\%.

>>>>

During a grid search of these parameters (in addition to regularization parameters of the network), the best accuracy achieved for replication of Acoustic Parameter was exactly 100\%. The mean of all epochs within that training run was 98\%.

Further demonstrating this is a powerful algorithm and that high performance was not a one-off, 35\% of the training runs replicated Acoustic Parameter with a mean accuracy greater than 92\% (shown in Figure \ref{icn_accuracy_by_run}.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{icn_accuracy_by_run}
    \caption{\label{icn_accuracy_by_run} Mean accuracy of iterative cluster nucleation configurations during grid search.}
\end{figure}
